The not so widening achievement gap: an interntational comparison of the evolution of the SES achievement gap from 2000-2015

### 2017-08-17 paper/paper.Rnw
Trying out the 75/25 gap

<<default_conf>>=
  library(knitr)
  library(arm)
  library(saves)
  library(haven)
  library(PISA2000lite)
  library(PISA2003lite)
  library(PISA2006lite)
  library(PISA2009lite)
  library(PISA2012lite)
  library(intsvy)
  library(cimentadaj) # devtools::install_github("cimentadaj/cimentadaj")
  library(countrycode) # For region variable
  library(car)
  library(SAScii)
  library(inequalityintsvy) # devtools::install_github("cimentadaj/inequalityintsvy")
  library(lme4)
  library(modelr)
  library(tidyverse)
  library(ggrepel)
  library(xtable)
  library(ggthemes)
  library(matrixStats)

@@

  pisa_all2$value[[6]] <-
    pisa_all2$value[[6]] %>%
    rename(escs_trend = ESCS)
@

@@

# results_math <- test_diff(adapted_year_data, reliability_pisa, "MATH", c(0.1, 0.9))
# results_read <- test_diff(adapted_year_data, reliability_pisa, "READ", c(0.1, 0.9))
# results_math_topmid <- test_diff(adapted_year_data, reliability_pisa, "MATH", c(0.5, 0.9))
# results_read_topmid <- test_diff(adapted_year_data, reliability_pisa, "READ", c(0.5, 0.9))
# results_math_midbottom <- test_diff(adapted_year_data, reliability_pisa, "MATH", c(0.1, 0.5))
# results_read_midbottom <- test_diff(adapted_year_data, reliability_pisa, "READ", c(0.1, 0.5))

results_math <- read_rds("./paper/data/delete.Rdata")
results_read <- read_rds("./paper/data/delete_read.Rdata")
results_math_topmid <- read_rds("./paper/data/delete_math_topmid.Rdata")
results_read_topmid <- read_rds("./paper/data/delete_read_topmid.Rdata")
results_math_midbottom <- read_rds("./paper/data/delete_math_midbottom.Rdata")
results_read_midbottom <- read_rds("./paper/data/delete_read_midbottom.Rdata")
# US is missing for reading

@@

escs_data <- escs_dummy_creator(adapted_year_data, c(0.1, 0.9))

@@

complete_data_topbottom <- mutate(complete_data_topbottom, type = "90th/10th SES gap")
complete_data_topmid <- mutate(complete_data_topmid, type = "90th/50th SES gap")
complete_data_midbottom <- mutate(complete_data_midbottom, type = "50th/10th SES gap")
@

@@

\begin{figure}
\begin{center}
<<graphing_9010gaps, include = T, out.height = '5in', out.width = '5.5in', fig.align = 'center'>>=
# 90/10 gaps acros countries
diff_increase_fun <- function(df) {

@@

<<>>=

@@

options(tibble.max_extra_cols = 10)
library(WDI)

@@

>>>>

<<default_conf>>=
library(knitr)
library(arm)
library(saves)
library(haven)
library(PISA2000lite)
library(PISA2003lite)
library(PISA2006lite)
library(PISA2009lite)
library(PISA2012lite)
library(intsvy)
library(cimentadaj) # devtools::install_github("cimentadaj/cimentadaj")
library(countrycode) # For region variable
library(car)
library(SAScii)
library(inequalityintsvy) # devtools::install_github("cimentadaj/inequalityintsvy")
library(lme4)
library(modelr)
library(tidyverse)
library(ggrepel)
library(xtable)
library(ggthemes)
library(matrixStats)
library(WDI)

@@

  pisa_all2$value[[6]] <-
    pisa_all2$value[[6]] %>%
    rename(escs_trend = escs_trend)
@

@@

results_math <- test_diff(adapted_year_data, reliability_pisa, "MATH", c(0.25, 0.75))
results_read <- test_diff(adapted_year_data, reliability_pisa, "READ", c(0.25, 0.75))
results_math_topmid <- test_diff(adapted_year_data, reliability_pisa, "MATH", c(0.5, 0.75))
results_read_topmid <- test_diff(adapted_year_data, reliability_pisa, "READ", c(0.5, 0.75))
results_math_midbottom <- test_diff(adapted_year_data, reliability_pisa, "MATH", c(0.25, 0.5))
results_read_midbottom <- test_diff(adapted_year_data, reliability_pisa, "READ", c(0.25, 0.5))

# results_math <- read_rds("./paper/data/delete.Rdata")
# results_read <- read_rds("./paper/data/delete_read.Rdata")
# results_math_topmid <- read_rds("./paper/data/delete_math_topmid.Rdata")
# results_read_topmid <- read_rds("./paper/data/delete_read_topmid.Rdata")
# results_math_midbottom <- read_rds("./paper/data/delete_math_midbottom.Rdata")
# results_read_midbottom <- read_rds("./paper/data/delete_read_midbottom.Rdata")
# US is missing for reading

@@

escs_data <- escs_dummy_creator(adapted_year_data, c(0.25, 0.75))

@@

complete_data_topbottom <- mutate(complete_data_topbottom, type = "75th/25th SES gap")
complete_data_topmid <- mutate(complete_data_topmid, type = "75th/50th SES gap")
complete_data_midbottom <- mutate(complete_data_midbottom, type = "50th/25th SES gap")
@

@@

\begin{figure}
\begin{center}
<<graphing_9010gaps, include = T, out.height = '5in', out.width = '5.5in', fig.align = 'center'>>=
# 90/10 gaps acros countries

df <- complete_data_topbottom

diff_increase_fun <- function(df) {

@@

<<eval = F>>=

@@

library(readxl)

@@

tracking_data <-
  readxl::read_xlsx("./paper/data/tracking.xlsx", sheet = "all_data") %>%
  map_if(is_double, round, 2) %>%
  as_tibble
